---
title: "Alcohol vs Seat choice"
author: "Quintin Burnett"
date: "Fall 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data
```{r}
basicCN <- ggplot(ucdavis1,aes(x=Seat,y=alcohol))
```
## Now add in boxplot
```{r}
basicCN + geom_boxplot()
```

The outliers in the "back" category is more than half than those in the "front". The median of the "back" category is higher than that of the "front". There is also a lot of outliers in the middle row.
  
### get fancy  
```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

This plot makes it easier to distinguish the medians of the "back" category and "front" category.

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=davisdata)
```

There about the same amount of people in the "Front" and "Back" categories. The "middle" has over the amount of both "front" and "back" combined. The "back" has a higher mean average than the "front" and "middle". The standard deviation of the "back" category is also substantially higher than the others.

## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The probability value is 0.000116. It is so small to get these results that something is going on in the different groups. We need to do more tests for more detailed results.

```{r}
plot(TukeyHSD(model1))
```

There is no significant difference for the "middle" category and the "front" so they are not different because 0 is a confidence. The "front" and "back" are different. The "middle" and "back" are different. What is important is that "back" is different from both.


## Conclusions

First I grabbed my ggplot code so I can run it after getting my table. I then grabbed another piece of code from the helper files to read that code and turn it into a boxplot. After I grabbed the numerical code to see the results including average. We then investigated the probability value in the t.test for inferential results. There we saw the probability was between 0-1 so we ran the one way anova since there were more than two things to compare. I grabbed the turkey test to show the differences in the mean of the "seats". There we concluded that "back" has more "alcohol" than the rest.
