---
title: "Alcohol vs Seat choice"
author: "Quintin Burnett"
date: "Fall 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data
```{r}
basicCN <- ggplot(ucdavis1,aes(x=Seat,y=alcohol))
```
## Now add in boxplot
```{r}
basicCN + geom_boxplot()
```

The outliers in the "back" category is more than half than those in the "front". The median of the "back" category is higher than that of the "front". There is also a lot of outliers in the middle row.
  
### get fancy  
```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

This plot makes it easier to distinguish the medians of the "back" category and "front" category.

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=davisdata)
```

There about the same amount of people in the "Front" and "Back" categories. The "middle" has over the amount of both "front" and "back" combined. The "back" has a higher mean average than the "front" and "middle". The standard deviation of the "back" category is also substantially higher than the others.

## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The probability value is 0.000116. It is so small to get these results that something is going on in the different groups. We need to do more tests for mor detailed results.

```{r}
plot(TukeyHSD(model1))
```

There is no significant difference for the "middle" category and the "front" so they are not different because 0 is a confidence. The "front" and "back" are different. The "middle" and "back" are different. What is important is that "back" is different from both.


## Conclusions


